Croder: Bringing the Knowledge of the Crowds into the IDE

### 2013-05-03 paper/paper.tex
added future work

\section{Crowds for software development}
One of the main challenges was finding the appropriate crowd to conduct the code review. One of the
first options was the Amazon Mechanical Turk. The main problem with this platform is the lack of
qualified workers. Code Reviewing is a very technical process that requires a large amount of knowledge.
We needed to aim for a platform where we were guaranteed to have the right audience.

@@

\begin{figure}[hbt]
	\centering
	\includegraphics[scale=0.3]{reviewBrowser.png}
\caption{Viewing code snippets}
\label{fig:snippetViewer}
\end{figure}

@@

>>>>

\section{Crowds for software development}
\label{sec:crowds}
One of the main challenges was finding the appropriate crowd to conduct the code review. One of the
first options was the Amazon Mechanical Turk. The main problem with this platform is the lack of
qualified workers. Code Reviewing is a very technical process that requires a large amount of knowledge.
We needed to aim for a platform where we were guaranteed to have the right audience.

@@

\begin{figure}[hbt]
	\centering
	\includegraphics[scale=0.4]{reviewBrowser.png}
\caption{Viewing code snippets}
\label{fig:snippetViewer}
\end{figure}

@@

Future work can be done in several directions.

The only platform currently used by \croder is Stackexchange code review due to reasons such as familiarity with the platform, constant activity and most importantly, it represents a crowd that is accustomed to the code review task type.
Future work in this regard would see \croder gain adapters for other platforms such as eLance or oDesk. On one hand, these platforms have mature APIs and sandboxed testing environments. On the other hand their crowds are not accustomed to micro-tasks.

%TODO fix section reference
Indeed, as was stated in section~\ref{sec:crowds}, eLance and oDesk crowds perform software outsourcing. Their tasks range from days to months and the compensation from tens to thousands of dollars. If we are to utilize these crowds then we shall have to experiment and see if we can get them accustomed to the micro-tasks of crowdsourcing. This implies that we will have to effectively teach the crowd. We shall have to start with oversized tasks and progressively decrease them in size and scope. We shall have to experiment with task size and compensation amount in order to find the sweet spots.

Automatic evaluation of crowdsourced reviews is also problematic. One cannot simply generate random code snippets of different size and complexity. Code snippets have to have a coherent story behind them otherwise the required specialized workers will not engage in their review.

Relating to code snippets, \croder currently leaves code snippet selection solely in the hands of the programmer. Unfortunately, while collecting the code to be reviewed, the programmer may miss essential snippets that complete the story of the review. We propose a semi automated approach in which \croder would suggest a least amount of additional snippets in order to have a more complete review. There are different solutions we can utilize in order to achieve this goal such as a metric based approach: a dependency and coupling analysis can be performed on the selected code snippets in order to find outside potential snippets that would minimize certain metrics.

In terms of the current implementation, particular code reviews are tied to only one \IDE installation. The feature to share and access the review results with other colleague's \IDE's would be most welcome.

Last but not least, code reviews represent only one possible software development task that can be crowdsourced. We identified several more, such as testing or on demand code transformations. In order to fully bring the knowledge of the crowds into the \IDE, \croder will have to learn how to crowdsource many more tasks, starting with the ones previously mentioned.
